Verifying Demonstrations

### 2019-07-16 paper/distance-bounding.tex
Improves comments on future DB protocols for DLs

% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
% Indeed, in this context it does not make sense to protect against the
% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
For this paper, we assume the existence of such a protocol. Candidates for such 
a protocol include modifications of~\cite{ProProx} or~\cite{PROPS} to work for 
discrete logarithm and to provide general attribute-based anonymous credentials 
(not restricted to identity-based ones), respectively.

>>>>

% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
% Indeed, in this context it does not make sense to protect against the
% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
For this paper, we assume the existence of such a protocol\footnote{%
  The authors have such a protocol under submission in another venue.
}.
There exists \ac{PPK} schemes, \eg~\cite{ProProx}, just not yet for discrete 
logarithms.
